{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-09 thesis/overview.tex
clean up some citation issues

\subsubsection{Shared state}
When a programming language offers multithreaded parallelism but forbids access to any shared state between threads \cite{rust-language},
the simultaneity of threads is largely irrelevant to the program's behaviour.
However, ``thread-unsafe'' languages such as C, C++, Java, and so on remain popular,
in which threads may access global or heap-allocated variables and data structures with no enforced access discipline.
The behaviour of such programs is then subject to the manner in which these accesses interleave.

>>>>

\subsubsection{Shared state}
When a programming language offers multithreaded parallelism but forbids access to any shared state between threads \cite{rust-book},
the simultaneity of threads is largely irrelevant to the program's behaviour.
However, ``thread-unsafe'' languages such as C, C++, Java, and so on remain popular,
in which threads may access global or heap-allocated variables and data structures with no enforced access discipline.
The behaviour of such programs is then subject to the manner in which these accesses interleave.

### 2018-12-09 thesis/thesis.tex
weak atomicity description, proof, & implementation, wee
clean up some citation issues

% some useful packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdwlist}
\usepackage[numbers,sort]{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage[backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
colorlinks=true,
citecolor=citec,
linkcolor=linkc,
urlcolor=urlc,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{microtype}
% "nosort" causes no sort AND no compress of 3+ section references in one;
% it's "sort" to sort but NOT compress; nothing to.. compress but not sort, i guess? not the greatest naming
\usepackage[nameinlink,nosort]{cleveref}

>>>>

% some useful packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mdwlist}
\usepackage[numbers,sort]{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage[backref=page,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
colorlinks=true,
citecolor=citec,
linkcolor=linkc,
urlcolor=urlc,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{microtype}
% "nosort" causes no sort AND no compress of 3+ section references in one;
% it's "sort" to sort but NOT compress; nothing to.. compress but not sort, i guess? not the greatest naming
\usepackage[nameinlink,nosort]{cleveref}
